CAKE: Classification \textit{avec} Kernel Embeddings \\ using Rademacher Complexity Bounds

### 2017-05-19 cake.tex
Separate main paper and supplementary material and fixed capital letters in references

@@

		\begin{table}[t]
			\caption{Classification Accuracy (\%) of Kernel Embedding Classifiers on UCI datasets}
			\label{tab:uci_experiments}
			\centering
			\begin{tabular}{lccccc}			
				Dataset \hspace{\fill} $(n, d, m)$ & GKEC & GKEC-SGD & KEN-1 & KEN-2 & Others \\
				\midrule
				\texttt{banknote} \hspace{\fill} (1372, 4, 2) & $99.9 \pm 0.2$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & 99.78\textsuperscript{a} \\
				\texttt{ecoli} \hspace{\fill} (336, 7, 8) & $87.5 \pm 4.4$ & $84.5 \pm 5.0$ & $87.5 \pm 3.2$ & $86.3 \pm 6.0$ & 81.1\textsuperscript{b} \\
				\texttt{robot} \hspace{\fill} (5456, 24, 4) & $96.7 \pm 0.9$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & 97.59\textsuperscript{c} \\
				\texttt{segment} \hspace{\fill} (2310, 19, 7) & $98.4 \pm 0.8$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & 96.83\textsuperscript{d} \\
				\texttt{wine} \hspace{\fill} (178, 13, 3) & $97.2 \pm 3.7$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & 100\textsuperscript{e} \\
				\texttt{yeast} \hspace{\fill} (1484, 8, 10) & $52.5 \pm 2.1$ & $60.3 \pm 4.4$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & 55.0\textsuperscript{b} \\
			\end{tabular}
		\end{table}

		We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels with explicit neural network features on standard UCI datasets \citep{merz1998uci}, summarised in \cref{tab:uci_experiments}. The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture. The Gaussian kernel is learned with both full (GKEC) and batch stochastic gradient updates (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each training iteration, with sensitivity and length scales initialised to $1$. For neural network induced kernels, we randomly select two simple fully connected architectures with 16-32-8 (KEN-1) and 96-32 (KEN-2) hidden units respectively, and learn the conditional embedding without dropout under ReLU activation. Biases and standard deviations of zero mean truncated normal distributed weights are initialised to $0.1$, and are to be trained with full gradient updates. For all experiments, $\lambda$ is initialised to $1$ and is learned jointly with the kernel. Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with rate $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$ \eqref{eq:learning_objective}. Classifiers are trained for 1000 or 10000 iterations when using full or batch gradient updates respectively, regardless of convergence. All attributes are scaled to the unit range. Each classifier is trained on 9 out of 10 folds and tested on the remaining fold, which are shuffled over all 10 combinations to obtain the test accuracy average and deviation. We compare our results to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}. \Cref{tab:uci_experiments} shows that our learning algorithm achieves similar performance without any special tuning or heuristics, but by simply placing a conditional embedding on training data and applying a complexity bound based learning algorithm. The SGD approach for Gaussian kernels performs similarly to the full gradient approach, supporting \cref{thm:expected_risk_bound_hyperparameter_learning_copy} for $n = n_{b}$. For neural network features, we did not attempt to choose an optimal architecture for each dataset. The learning algorithm is to train the same simple untrained network for different datasets under only 1000 iterations, and still generates comparable performance.

@@

\newpage
\appendix

\section{Convergence Theorems for Kernel Embedding Classifiers}
\label{app:convergence_theorems}

	In this section we provide theorems, lemmas, and derivations for the convergence properties of the kernel embedding classifier.

	We consider the case in which a dataset, represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$, is collected in a \textit{iid} fashion from some distribution $\mathbb{P}_{X Y}$. That is $\{X_{i}, Y_{i}\} \sim \mathbb{P}_{X Y}$ for all $i \in \mathbb{N}_{n}$ and each observed sample is independent from each other. Suppose we have an estimator function $\hat{f}^{(n)} : \mathcal{X} \to \mathbb{R}$ which is to estimate some target function  $f : \mathcal{X} \to \mathbb{R}$, usually but not necessarily derived from $\mathbb{P}_{Y |X }$, empirically using the collected dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of size $n \in \mathbb{N}_{+}$. Here, we use the superscript $(n)$ to denote the estimator's dependence on the dataset. From this point on, we drop this superscript to avoid cluttered notation. However, one should keep in mind that $\hat{f}$ is estimated using the dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ and is thus random over the possible data observation events $\omega \in \Omega$. We would like to provide a sense of the stochastic convergence of $\hat{f}$ to $f$ by providing an upper bound of their absolute pointwise difference $| \hat{f}(x) - f(x) |$, and show that such an upper bound converges to zero at some stochastic rate. Since the kernel embedding classifier is based on conditional embeddings (and, as we will show, is equivalent to a conditional embedding), this upper bound will be provided by the RKHS norm of the error between empirical and true conditional embeddings. Specifically, the empirical conditional embedding stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}. That is,
	\begin{equation}
		\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t. \quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
	\label{eq:empirical_conditional_embedding_stochastic_convergence}
	\end{equation}
	\begin{theorem}[Pointwise and Uniform Convergence of Estimators based on Conditional Embeddings]
		\label{thm:pointwise_uniform_convergence}
		Suppose that $k(x, \cdot)$ is in the image of $C_{XX}$ and that there exists $0 \leq \gamma(x) < \infty$ such that for some estimator function $\hat{f} : \mathcal{X} \to \mathbb{R}$ and target function  $f : \mathcal{X} \to \mathbb{R}$,
		\begin{equation}
			| \hat{f}(x) - f(x) | \leq \gamma(x) \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}}, \forall x \in \mathcal{X},
		\label{eq:estimator_error_bound}
		\end{equation}
		then the estimator $\hat{f}$ converges pointwise to the target $f$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. Further, if $\gamma(x) = \gamma$ is independent of $x \in \mathcal{X}$, then this convergence is uniform.

		\begin{proof}

			Suppose that there exists $0 \leq \gamma(x) < \infty$ such that \eqref{eq:estimator_error_bound} is satisfied. That is, the inequality \eqref{eq:estimator_error_bound} holds for all possible data observations $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$. For any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{f}(x) - f(x) | \leq C \gamma(x)$ holds for all possible observation events $\omega \in \Omega$. Writing this explicitly in event space translates this to a probability statement,
			\begin{equation}
			\begin{aligned}
				\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{f}(x) - f(x) | \leq C \gamma(x)\} \\
				\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq C \gamma(x) \Big].
			\label{eq:probability_statement}
			\end{aligned}
			\end{equation}
			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid. By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{f}(x) - f(x) |$ and $M_{\epsilon}$ with $\gamma(x) M_{\epsilon}$,
			\begin{equation}
			\begin{aligned}
			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
			\implies 1 - \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | > \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
			\end{aligned}	
			\end{equation}
			where we employed statement \eqref{eq:probability_statement} between the third and fourth line for $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. Therefore, since $M_{\epsilon}$ is arbitrary, define $\tilde{M}_{\epsilon}(x) := \gamma(x) M_{\epsilon}$ so that, with the above result, the statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} implies the following,
			\begin{equation}
				\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists \tilde{M}_{\epsilon}(x) > 0 \quad s.t. \quad \mathbb{P}\Big[\big| \hat{f}(x) - f(x) \big| > \tilde{M}_{\epsilon}(x) \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
			\end{equation}
			In other words, the function $\hat{f}$ stochastically converges pointwise to $f$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. The convergence is pointwise as the constant $\tilde{M}_{\epsilon}(x)$ may be different for each point $x \in \mathcal{X}$. If $\gamma(x) = \gamma$ such that $\tilde{M}_{\epsilon}(x) = \tilde{M}_{\epsilon}$ does not depend on $x \in \mathcal{X}$, then this stochastic convergence is uniform in its domain $\mathcal{X}$.
		\end{proof}

	\end{theorem}

	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the RKHS norm. As such, we turn to the convergence of the empirical decision probability function \eqref{eq:empirical_decision_probability} below.

	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
		\label{thm:probability_convergence}
		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.

		\begin{proof}

			Consider the pointwise absolute difference between the decision probability and its empirical estimate,
			\begin{equation}
				\begin{aligned}
					| \hat{p}_{c}(x) - p_{c}(x) | &= | \langle \hat{\mu}_{Y | X = x}, \mathbb{1}_{c} \rangle - \langle \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
					&= | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
					&\leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}},
				\label{eq:decision_probability_error_upper_bound}
				\end{aligned}
			\end{equation}
			where the last inequality follows from the Cauchy Schwarz inequality in a Hilbert space.

			From \eqref{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
			\begin{equation}
				\begin{aligned}
					\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
				\label{eq:indicator_rkhs_norm}
				\end{aligned}
			\end{equation}
			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, $\hat{p}_{c}$ converges uniformly to $p_{c}$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.

		\end{proof}
	\end{theorem}

	The above proof is for uniform convergence over all $x \in \mathcal{X}$ at the stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. Intuitively, however, for stationary zero-centred kernels like the Gaussian kernel, the convergence rate may be higher at regions of high data density, since the kernel effects, being centred around the training data, are stronger at these regions. The worse case convergence rate described here in the theorem would be a tight lower bound for regions in $\mathcal{X}$ with lower data density, where the kernel effects have decayed and most empirical probabilities are smaller and further from summing up to one.

>>>>

%\usepackage{varioref}
%\usepackage{xr-hyper}
%\externaldocument[cake_appendix]{cake_appendix}

@@

		\begin{table}[t]
			\caption{Classification accuracy (\%) of kernel embedding classifiers on UCI datasets}
			\label{tab:uci_experiments}
			\centering
			\begin{tabular}{lccccc}			
				Dataset \hspace{\fill} $(n, d, m)$ & GKEC & GKEC-SGD & KEN-1 & KEN-2 & Others \\
				\midrule
				\texttt{banknote} \hspace{\fill} (1372, 4, 2) & $99.9 \pm 0.2$ & $98.8 \pm 0.9$ & $99.5 \pm 1.0$ & $99.4 \pm 0.9$ & 99.78\textsuperscript{a} \\
				\texttt{ecoli} \hspace{\fill} (336, 7, 8) & $87.5 \pm 4.4$ & $84.5 \pm 5.0$ & $87.5 \pm 3.2$ & $86.3 \pm 6.0$ & 81.1\textsuperscript{b} \\
				\texttt{robot} \hspace{\fill} (5456, 24, 4) & $96.7 \pm 0.9$ & $95.5 \pm 0.9$ & $82.3 \pm 7.1$ & $94.5 \pm 0.8$ & 97.59\textsuperscript{c} \\
				\texttt{segment} \hspace{\fill} (2310, 19, 7) & $98.4 \pm 0.8$ & $96.1 \pm 1.5$ & $94.6 \pm 1.6$ & $96.7 \pm 1.1$ & 96.83\textsuperscript{d} \\
				\texttt{wine} \hspace{\fill} (178, 13, 3) & $97.2 \pm 3.7$ & $93.3 \pm 6.0$ & $96.1 \pm 5.0$ & $97.2 \pm 5.1$ & 100\textsuperscript{e} \\
				\texttt{yeast} \hspace{\fill} (1484, 8, 10) & $52.5 \pm 2.1$ & $60.3 \pm 4.4$ & $55.8 \pm 5.0$ & $59.6 \pm 4.0$ & 55.0\textsuperscript{b} \\
			\end{tabular}
		\end{table}

		We demonstrate the average performance of learning anisotropic Gaussian kernels and kernels with explicit neural network features on standard UCI datasets \citep{bache2013uci}, summarised in \cref{tab:uci_experiments}. The former has a shallow but wide model architecture, while the latter has a deeper but narrower model architecture. The Gaussian kernel is learned with both full (GKEC) and batch stochastic gradient updates (GKEC-SGD) using a tenth ($n_{b} \approx \frac{n}{10}$) of the training set each training iteration, with sensitivity and length scales initialised to $1$. For neural network induced kernels, we randomly select two simple fully connected architectures with 16-32-8 (KEN-1) and 96-32 (KEN-2) hidden units respectively, and learn the conditional embedding without dropout under ReLU activation. Biases and standard deviations of zero mean truncated normal distributed weights are initialised to $0.1$, and are to be trained with full gradient updates. For all experiments, $\lambda$ is initialised to $1$ and is learned jointly with the kernel. Classifiers are trained with the Adam optimiser \citep{kingma2014adam} in TensorFlow \citep{abadi2016tensorflow} with rate $\eta = 0.1$ and $\epsilon = 10^{-15}$ under the learning objective $q(\theta, \lambda)$ \eqref{eq:learning_objective}. Classifiers are trained for 1000 or 10000 iterations when using full or batch gradient updates respectively, regardless of convergence. All attributes are scaled to the unit range. Each classifier is trained on 9 out of 10 folds and tested on the remaining fold, which are shuffled over all 10 combinations to obtain the test accuracy average and deviation. We compare our results to other approaches using neural networks \citep[a; c]{kaya2016banknote, freire2009short}, probabilistic binary trees \citep[b]{horton1996probabilistic}, decision trees \citep[d]{zhou2004size}, and regularised discriminant analysis \citep[e]{aeberhard1992comparison}. \Cref{tab:uci_experiments} shows that our learning algorithm achieves similar performance without any special tuning or heuristics, but by simply placing a conditional embedding on training data and applying a complexity bound based learning algorithm. The SGD approach for Gaussian kernels performs similarly to the full gradient approach, supporting \cref{thm:expected_risk_bound_hyperparameter_learning_copy} for $n = n_{b}$. For neural network features, we did not attempt to choose an optimal architecture for each dataset. The learning algorithm is to train the same simple untrained network for different datasets under only 1000 iterations, and still generates comparable performance.

@@

%\newpage
%\appendix
%	
%\section{Convergence Theorems for Kernel Embedding Classifiers}
%\label{app:convergence_theorems}
%
%	In this section we provide theorems, lemmas, and derivations for the convergence properties of the kernel embedding classifier.
%	
%	We consider the case in which a dataset, represented by the collection of random variables $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$, is collected in a \textit{iid} fashion from some distribution $\mathbb{P}_{X Y}$. That is $\{X_{i}, Y_{i}\} \sim \mathbb{P}_{X Y}$ for all $i \in \mathbb{N}_{n}$ and each observed sample is independent from each other. Suppose we have an estimator function $\hat{f}^{(n)} : \mathcal{X} \to \mathbb{R}$ which is to estimate some target function  $f : \mathcal{X} \to \mathbb{R}$, usually but not necessarily derived from $\mathbb{P}_{Y |X }$, empirically using the collected dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ of size $n \in \mathbb{N}_{+}$. Here, we use the superscript $(n)$ to denote the estimator's dependence on the dataset. From this point on, we drop this superscript to avoid cluttered notation. However, one should keep in mind that $\hat{f}$ is estimated using the dataset $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ and is thus random over the possible data observation events $\omega \in \Omega$. We would like to provide a sense of the stochastic convergence of $\hat{f}$ to $f$ by providing an upper bound of their absolute pointwise difference $| \hat{f}(x) - f(x) |$, and show that such an upper bound converges to zero at some stochastic rate. Since the kernel embedding classifier is based on conditional embeddings (and, as we will show, is equivalent to a conditional embedding), this upper bound will be provided by the RKHS norm of the error between empirical and true conditional embeddings. Specifically, the empirical conditional embedding stochastically converges to the true conditional embedding $\mu_{Y | X = x}$ in the RKHS norm at a rate of $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$, under the assumption that $k(x, \cdot)$ is in the image of $C_{XX}$ \cite[Theorem 6]{song2009hilbert}. That is,
%	\begin{equation}
%		\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists M_{\epsilon} > 0 \quad s.t. \quad \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
%	\label{eq:empirical_conditional_embedding_stochastic_convergence}
%	\end{equation}
%	\begin{theorem}[Pointwise and Uniform Convergence of Estimators based on Conditional Embeddings]
%		\label{thm:pointwise_uniform_convergence}
%		Suppose that $k(x, \cdot)$ is in the image of $C_{XX}$ and that there exists $0 \leq \gamma(x) < \infty$ such that for some estimator function $\hat{f} : \mathcal{X} \to \mathbb{R}$ and target function  $f : \mathcal{X} \to \mathbb{R}$,
%		\begin{equation}
%			| \hat{f}(x) - f(x) | \leq \gamma(x) \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}}, \forall x \in \mathcal{X},
%		\label{eq:estimator_error_bound}
%		\end{equation}
%		then the estimator $\hat{f}$ converges pointwise to the target $f$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. Further, if $\gamma(x) = \gamma$ is independent of $x \in \mathcal{X}$, then this convergence is uniform.
%		
%		\begin{proof}
%			
%			Suppose that there exists $0 \leq \gamma(x) < \infty$ such that \eqref{eq:estimator_error_bound} is satisfied. That is, the inequality \eqref{eq:estimator_error_bound} holds for all possible data observations $\{X_{i}, Y_{i}\}_{i = 1}^{n}$ where $X_{i} : \Omega \to \mathcal{X}$,  $Y_{i} : \Omega \to \mathcal{Y}$ for all $i \in \mathbb{N}_{n}$. For any constant $C$, the implication statement $\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \leq C \implies | \hat{f}(x) - f(x) | \leq C \gamma(x)$ holds for all possible observation events $\omega \in \Omega$. Writing this explicitly in event space translates this to a probability statement,
%			\begin{equation}
%			\begin{aligned}
%				\{\omega \in \Omega : \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\} &\subseteq \{\omega \in \Omega : | \hat{f}(x) - f(x) | \leq C \gamma(x)\} \\
%				\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq C\Big] &\leq \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq C \gamma(x) \Big].
%			\label{eq:probability_statement}
%			\end{aligned}
%			\end{equation}
%			Since we assume that $k(x, \cdot) \in \mathrm{image}(C_{XX})$, statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is valid. By letting $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ in \eqref{eq:probability_statement}, we immediately have that the probability inequality in statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} is also true if we replace $\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \|$ with $| \hat{f}(x) - f(x) |$ and $M_{\epsilon}$ with $\gamma(x) M_{\epsilon}$,
%			\begin{equation}
%			\begin{aligned}
%			\mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} > M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
%			\implies 1 - \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
%			\implies \mathbb{P}\Big[\big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{l}} \leq M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
%			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &> 1 -  \epsilon \\
%			\implies 1 - \mathbb{P}\Big[| \hat{f}(x) - f(x) | \leq \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon \\
%			\implies \mathbb{P}\Big[| \hat{f}(x) - f(x) | > \gamma(x) M_{\epsilon} \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] &< \epsilon.
%			\end{aligned}	
%			\end{equation}
%			where we employed statement \eqref{eq:probability_statement} between the third and fourth line for $C = M_{\epsilon} ((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. Therefore, since $M_{\epsilon}$ is arbitrary, define $\tilde{M}_{\epsilon}(x) := \gamma(x) M_{\epsilon}$ so that, with the above result, the statement \eqref{eq:empirical_conditional_embedding_stochastic_convergence} implies the following,
%			\begin{equation}
%				\forall x \in \mathcal{X}, \; \epsilon > 0, \; \exists \tilde{M}_{\epsilon}(x) > 0 \quad s.t. \quad \mathbb{P}\Big[\big| \hat{f}(x) - f(x) \big| > \tilde{M}_{\epsilon}(x) \Big((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}}\Big)\Big] < \epsilon.
%			\end{equation}
%			In other words, the function $\hat{f}$ stochastically converges pointwise to $f$ with a rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. The convergence is pointwise as the constant $\tilde{M}_{\epsilon}(x)$ may be different for each point $x \in \mathcal{X}$. If $\gamma(x) = \gamma$ such that $\tilde{M}_{\epsilon}(x) = \tilde{M}_{\epsilon}$ does not depend on $x \in \mathcal{X}$, then this stochastic convergence is uniform in its domain $\mathcal{X}$.
%		\end{proof}
%
%	\end{theorem}
%	
%	With \cref{thm:pointwise_uniform_convergence}, we can now show the convergence of various estimators based on the conditional embedding, as long as we can show that their estimator error is upper bounded by a multiple of the conditional embedding error in the RKHS norm. As such, we turn to the convergence of the empirical decision probability function \eqref{eq:empirical_decision_probability} below.
%
%	\begin{theorem}[Uniform Convergence of Empirical Decision Probability Function]
%		\label{thm:probability_convergence}
%		Assuming that $k(x, \cdot)$ is in the image of $C_{XX}$, the empirical decision probability function $\hat{p}_{c} : \mathcal{X} \to \mathbb{R}$ \eqref{eq:empirical_decision_probability} converges uniformly to the true decision probability $p_{c} : \mathcal{X} \to [0, 1]$ \eqref{eq:decision_probability} at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
%		
%		\begin{proof}
%
%			Consider the pointwise absolute difference between the decision probability and its empirical estimate,
%			\begin{equation}
%				\begin{aligned}
%					| \hat{p}_{c}(x) - p_{c}(x) | &= | \langle \hat{\mu}_{Y | X = x}, \mathbb{1}_{c} \rangle - \langle \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
%					&= | \langle \hat{\mu}_{Y | X = x} - \mu_{Y | X = x}, \mathbb{1}_{c} \rangle | \\
%					&\leq \big\| \hat{\mu}_{Y | X = x} - \mu_{Y | X = x} \big\|_{\mathcal{H}_{\delta}} \big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}},
%				\label{eq:decision_probability_error_upper_bound}
%				\end{aligned}
%			\end{equation}
%			where the last inequality follows from the Cauchy Schwarz inequality in a Hilbert space.
%			
%			From \eqref{eq:indicator_function}, since $\mathbb{1}_{c} = \delta(c, \cdot)$ and using the fact that $\delta$ is a reproducing kernel, we have that for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
%			\begin{equation}
%				\begin{aligned}
%					\big\| \mathbb{1}_{c} \big\|_{\mathcal{H}_{\delta}}^{2} = \langle \mathbb{1}_{c}, \mathbb{1}_{c} \rangle = \langle \delta(c, \cdot), \delta(c, \cdot) \rangle = \delta(c, c) = 1.
%				\label{eq:indicator_rkhs_norm}
%				\end{aligned}
%			\end{equation}
%			Therefore, by \cref{thm:pointwise_uniform_convergence} with $\gamma(x) = 1$ independent of $x \in \mathcal{X}$, $\hat{p}_{c}$ converges uniformly to $p_{c}$ at a stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$ for all $c \in \mathcal{Y} = \mathbb{N}_{m}$.
%			
%		\end{proof}
%	\end{theorem}
%	
%	The above proof is for uniform convergence over all $x \in \mathcal{X}$ at the stochastic rate of at least $O_{p}((n \lambda)^{-\frac{1}{2}} + \lambda^{\frac{1}{2}})$. Intuitively, however, for stationary zero-centred kernels like the Gaussian kernel, the convergence rate may be higher at regions of high data density, since the kernel effects, being centred around the training data, are stronger at these regions. The worse case convergence rate described here in the theorem would be a tight lower bound for regions in $\mathcal{X}$ with lower data density, where the kernel effects have decayed and most empirical probabilities are smaller and further from summing up to one.
%	
%	Because the label space $\mathcal{Y} = \mathbb{N}_{m}$ is discrete and finite, \textit{bounded} functions $g \in \mathcal{H}_{\delta}$ in the RKHS are actually equivalent to their vector representations $\bvec{g} := \{g(c)\}_{c = 1}^{m}$, because one can always write $g = \sum_{c = 1}^{m} g(c) \delta(c, \cdot)$. This immediately implies that inner products in this space are simply the usual dot products in a Euclidean space, since
%	\begin{equation}
%		\begin{aligned}
%			\langle g_{1}, g_{2} \rangle_{\mathcal{H}_{\delta}} &= \bigg\langle \sum_{c = 1}^{m} g_{1}(c) \delta(c, \cdot), \sum_{c' = 1}^{m} g_{2}(c') \delta(c', \cdot)  \bigg\rangle_{\mathcal{H}_{\delta}} \\
